Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-06-05 SDSS Presentation/SDSS Presentation.Rmd
Screenshot updates and Susan comments

---
# Rural Shrink Smart Project
.center[
![](Shrink_Smart_logo.png)
]
.center[
(https://ruralshrinksmart.org/)
]

@@

+ .emph.cerulean[The Rural Shrink Smart EDA dashboard incorporates two major components]: 
    + Data Visualization Interface component with Guided Discovery Learning (GDL) principles, which engages the town leaders. 
    + Exploratory Data Analysis component utilizing statistical clustering methods, which allow town leaders the opportunity explore new elements to add or remove.

@@

+ <span style="color:darkred">Project Question:</span> How do we leverage <span style="color:blue">data science</span>  and <span style="color:blue">exploratory data methods</span> to inform town leaders to reduce the shrinkage and maintain reliability?
    + Can traditional dashboard design of open source data be incorporated into overall decision-making?
    + Can we focus on estimating only things that objective measurements don't capture?

@@

<br>
.large.emph[
+ Version 2: After implementation has been completed and the team notes limitations, we change the interface.
]

<br>
.large.emph[
+ Version 3: Now incorporate more literature on dashboard design and user experience, which removes some of the "cool" implementations 
]

<br>
.large.emph[
+ Version 4: Finally incorporate a collective feedback from team-leaders that suggests lack of understanding of information
]

@@

.large.emph[
+ Paralllel Coordinate Plot with objective measures related to the QoL Survey
]

@@

      + e.g. "I'm having a hard time understanding the PCP information", we will see that users are not spending any time on the PCP plot.
---
class:primary

@@

+ Allow the....???

>>>>

---
# Rural Shrink Smart Project
.center[
<img src="images/Shrink_Smart_logo.png" width="35%"/>
]

@@

+ .emph.cerulean[The Rural Shrink Smart EDA dashboard incorporates two major components]: 
    + Data Visualization Interface component with Guided Discovery Learning (GDL) principles
    + Exploratory Data Analysis component utilizing statistical graphical elements, such as maps and Parallel Coordinate Plots (PCPs)

@@

+ <span style="color:darkred">Project Question:</span> How do we leverage <span style="color:blue">data science</span>  and <span style="color:blue">exploratory data methods</span> to inform town leaders to reduce the shrinkage and maintain reliability?
    + How does an interactive dashboard of open-source data integrate into overall decision-making?
    + Can we focus on estimating only things that objective measurements don't capture?

@@

.center[
<img src="images/version1.png" width="75%"/>
]

.large.emph[
+ Version 2: After implementation has been completed and the team notes limitations, we change the interface.
]

.center[
<img src="images/version2.png" width="75%"/>
]

.large.emph[
+ Version 3: Now incorporate more literature on dashboard design and user experience, which removes some of the "cool" implementations 
]

.center[
<img src="images/version3.png" width="50%"/>
]

.large.emph[
+ Version 4: Finally incorporate a collective feedback from team-leaders that suggests lack of understanding of information
]

.center[
<img src="images/version4.png" width="75%"/>
]

@@

.large.emph[
+ Parallel Coordinate Plot with objective measures related to the QoL Survey
]

@@

      + e.g. "I'm having a hard time understanding the PCP information", we will see that users are not spending any time on the PCP.

.center[
<img src="images/feedback_question.png" width="35%"/>
]
---
class:primary

@@

+ Continue to incorporate feedback from town leaders.
<br>
.center[
<img src="images/feedback_loop.png" width="50%"/>
]
